Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-20 reanalysis-4-outcome_analysis.qmd
graph remove
final

# ANALYSIS MODE: Use same as imputation/PS
analysis_mode <- "test"  # Should match imputation and PS modes

@@

@@

@@

# Display the plot
print(forest_plot)

@@

print(forest_plot_annotated)
```

>>>>

# ANALYSIS MODE: Use same as imputation/PS
analysis_mode <- "final"  # Should match imputation and PS modes

@@

::: {.callout-note collapse="true"}
## Click to expand manual calculations

This section shows the manual calculation of subgroup effects for validation purposes.

@@

:::

@@

@@

# Display the annotated plot
forest_plot_annotated
```
